\RequirePackage{lineno}

\documentclass[onecolumn,aps,prd,groupedaddress,nofootinbib,notitlepage,12pt]{revtex4-1}
%\documentclass[onecolumn,aps,prd,groupedaddress,nofootinbib,notitlepage,12pt]{revtex4}
%\documentclass[preprint,onecolumn,aps,prd,groupedaddress,nofootinbib,notitlepage]{revtex4}
\usepackage{graphicx}
%\graphicspath{{figures/}} \DeclareGraphicsExtensions{.eps}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{slashed}
%\usepackage[hypertex]{hyperref}
\usepackage{xcolor}
\usepackage{amsfonts}
\usepackage{soul}
\usepackage[normalem]{ulem}

%\allowdisplaybreaks allows page breaks inside environment such as align.
\allowdisplaybreaks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    											  %%
%%                           		titles 							  %%
%%    											  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Reviews}

\author{Jing Qian (jq2282)}
%\email{qianjing8758@gmail.com}
%\affiliation{Department of Physics, The Ohio State University, Columbus, Ohio 43210, USA}

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{First draft}
1. Definition and history of flipped classroom.
#around the world, cover different majors->chemistry, education, CS, medical...

2. People's research history of flipped classroom.

3. Student's view of flipped classroom.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Flipped Courses}
review :
https://pdfs.semanticscholar.org/5710/14a2d984dbfeea58f68b28860a07e59047dc.pdf?_ga=2.119126144.889857229.1550502378-336897620.1550502378
\\\\
2. Do students like the flipped classroom? An investigation of student reaction to a flipped undergraduate IT course (2014)

https://www.semanticscholar.org/paper/Do-students-like-the-flipped-classroom-An-of-to-a-Elliott/7e877481ac9ae33d25b404796d86258e61528f17

说的含糊，combines successful techniques for distance education with constructivist learning theory in the classroom. 但说是significant improvement in learning outcomes.
\\\\
2.*. similarly, china, zhejiang university, 15 undergraduate education major students,  students satisfied with many aspects, but not interaction with others. https://online-journals.org/index.php/i-jet/article/view/4708

\\\\
3. The flipped classroom: for active, effective and increased learning – especially for low achievers (2016)

http://educationaltechnologyjournal.springeropen.com/articles/10.1186/s41239-016-0032-z

Questionnaire, majority positive.  Low achievers significantly reported more positively.
\\\\
5.  Performance and perception in the flipped classroom (2016)

https://link.springer.com/article/10.1007\%2Fs10639-015-9393-5

University of the West Indies, undergraduate, two successive years -- 1 traditional vs. 1 flip.
Evaluate learning experience -> exam performance & student perception.
Grades vs. student perception.
qualitative -> slight improvement on perception, quantitative -> no significant change in grade, fewer highest remarks.
\\\\
6. Implementing the flipped classroom: an exploration of study behaviour and student performance (2016)

https://pdfs.semanticscholar.org/4005/8eb035a8821edd7392a12ce6ee576a74d1e0.pdf?_ga=2.89775250.889857229.1550502378-336897620.1550502378

learning behavior-> bi-weekly diaries. 
study behavior similar with regular, but behavior not strongly related to performance.
Some resistance to change behavior.


\\\\
4. The Flipped-Classroom Approach: The Answer to Future Learning? (2014)

https://www.semanticscholar.org/paper/The-Flipped-Classroom-Approach\%3A-The-Answer-to-Kurtz-Tsimerman/151f1ad5f1465d5c0cb53a939366df5e5cc16990

Isreal, quesionnaire,  business undergraduate.
Positive attitude.
Better: in class, non-worker, female, older, have classmate nearby
\\\\
1. Student views on the use of flipped learning in higher education: A pilot study (2019)

https://link.springer.com/article/10.1007\%2Fs10639-019-09881-8

Pilot study. Questionnaire from students.
Pros: flexibility, responsible. 
Cons: lack immediate feedback \& poor internet accessibility.
\\\\
7. Faculty Support for Effective Flipped Classrooms in Higher Education (2017)

https://www.semanticscholar.org/paper/Faculty-Support-for-Effective-Flipped-Classrooms-in-Iwasaki/2a4aa7bbeb9c7ce3db791feb7cc482e707d5a9b6

Japan, questionnaire survey\&interview of  faculty

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{增进学习结果——游戏}
1. Applying learning analytics to students’ interaction in business simulation games. The usefulness of learning analytics to know what students really learn (2019)

https://dl.acm.org/citation.cfm?doid=3282844
\\\\
2. Learning IS Child's Play: Game-Based Learning in Computer Science Education (2019)

https://dl.acm.org/citation.cfm?doid=3282844


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Online Learner Behavior}
1. Data-driven unsupervised clustering of online learner behaviour (2019)

https://arxiv.org/pdf/1902.04047.pdf

Time sesires analysis and clustering groups of learners. 
Identify high and low performance learners.
\\\\
2. Democratizing education? Examining access and usage patterns in massive open online courses (2015)

http://science.sciencemag.org/content/350/6265/1245

68 MOOCs offered by Harvard and MIT between 2012 and 2014.
Participants from more-affluent and better-educated neighborhoods, finishers with greater socioeconomic resources.
Larger difference for youngs.
Conclusion: online learning excerbate disparities in education.

* Many papers about MOOC, like characteristics of MOOC (https://www.semanticscholar.org/paper/A-Systematic-Analysis-and-Synthesis-of-the-MOOC-in-Veletsianos/84c936fed5829c1c9252efc1f9a05602a23e3e8f, ), why people drop out courses (https://www.semanticscholar.org/paper/Interaction-and-Student-Dropout-in-Massive-Open-Harju-Lepp\%C3\%A4nen/cc8bbbc8d621523ccf7ef2323458648298126986), influencing factors (https://www.semanticscholar.org/paper/Mapping-the-Factors-Influencing-Success-of-Massive-Albelbisi-Yusop/4fcb2e93227c02bf112875e2ed017db601904df2)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Online learning with degrees -- Distance Learning}
1. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Others}
1. Expectations, Challenges and Suggestions for Faculty Teaching Online Courses in Higher Education (2019)

https://www.igi-global.com/gateway/article/216932

美国四所中西部大学教授在线课程的17名教师收集的数据。
在线教师面临的主要挑战是：大班教学，学术不诚实，与学生缺乏联系，电子邮件太多，缺乏学生自律。
该研究为在线教师提供可行的专业发展，作为在线课程教学的先决条件。
\\\\
2. Handbook of Research on Blended Learning Pedagogies and Professional Development in Higher Education (2019)

https://www.igi-global.com/gateway/book/190385

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               %
%          References           %
%  						  	    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{thebibliography}{99}

%\bibliography{./references/mybibliography}
\end{thebibliography}

%======================= The End =================================
\end{document}

